---
title: "American Actors and their affiliation with movie revenue generation"
author: "Mogens Yde-Andersen"
date: "20. sep. 2015"
output:
  html_document:
    theme: united
    toc: yes
  md_document:
    toc: yes
  word_document: default
---
###Gross revenues for US actors
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

2 Load processed data publicized from IMDB website
```{r 2, echo=FALSE, cache=TRUE}
library(devtools)
library(ggplot2)
actors <- read.csv("data/IMDBactors4D.csv", header=TRUE, sep=";")
```

2AA Load processed data publicized from IMDB website
#```{r 2AA, echo=FALSE, cache=TRUE}
#
# summary(actors)
# str(actors)
# head(actors,15)
# tail(actors,15)
# ```

2A
```{r 2A, echo=FALSE, cache=TRUE}
 actors$movies <- as.numeric(as.character(actors$movies))
```
 
2B
```{r 2B, echo=FALSE, cache=TRUE}
actors$totalRevenue <- as.numeric(as.character(actors$totalRevenue))
```

2C
```{r 2C, echo=FALSE, cache=TRUE}
actors$avRevenue <- as.numeric(as.character(actors$avRevenue))
```

2D
```{r 2D, echo=FALSE, cache=TRUE}
actors$topMovieRevenue <- as.numeric(as.character(actors$topMovieRevenue))
```
 
#2E
# ```{r 2E, echo=FALSE, cache=TRUE}
# actors$no1Mov <- actors$number1Movie
# ```
# 
# 2E2
# ```{r 2E2, echo=FALSE, cache=TRUE}
# actors <- actors[,c(1,5,7:11)]
# ```

2K
```{r 2K, echo=FALSE, cache=TRUE}
summary(actors)
str(actors)
head(actors,15)
tail(actors,15)
```

Dimensions
```{r 3 dim, echo=FALSE, cache=TRUE}
dim(actors)
```
3 Structure and overviewe of data set
```{r 3, echo=FALSE, cache=TRUE}
str(actors)
summary(actors)
```
4 Head and tail of variables
```{r 4, echo=FALSE, cache=TRUE}
head(actors$actor)
tail(actors$actor)
head(actors$totalRevenue)
tail(actors$totalRevenue)
head(actors$movies)
tail(actors$movies)
head(actors$avRevenue)
tail(actors$avRevenue)
head(actors$topMovie)
tail(actors$topMovie)
head(actors$topMovieRevenue)
tail(actors$topMovieRevenue)

table(actors$totalRevenue)
table(actors$movies)
table(actors$avRevenue)
table(actors$topMovieRevenue)
```

5 Histograms of GrossRevenue variables
```{r 5, echo=FALSE, cache=TRUE}
hist(actors$totalRevenue,breaks = 30, col.bars = actors$sex)
```

5A
```{r 5A, echo=FALSE, cache=TRUE}
hist(actors$movies,breaks = 74)
```

5B
```{r 5B, echo=FALSE, cache=TRUE}
hist(actors$avRevenue,breaks=11)
```

5C
##```{r 5C, echo=FALSE, cache=TRUE}
##hist(actors$topMovieRevenue,breaks=11)
##```

6 Exploratory plot
```{r 6, echo=FALSE, cache=TRUE}
plot(actors)
```

7A Total Gross Revenue per actor by number of movies and by sex
```{r 7A, echo=FALSE, cache=TRUE}
library(ggplot2)
f <- ggplot(actors, aes(x=movies,y=totalRevenue, colour = sex))
f <- f + geom_hline(yintercept = 1000,size=1,col="deepskyblue")
f <- f + geom_vline(xintercept = 18.58,size=1,col="deepskyblue")
f <- f + geom_point(size = 2)
f
```

7 Total Gross Revenue per actor by number of movies
```{r 7, echo=FALSE, cache=TRUE}
g <- ggplot(actors, aes(x = movies,y = totalRevenue))
g <- g + geom_hline(yintercept = 358,size=1,col="deepskyblue")
g <- g + geom_vline(xintercept = 18.58,size=1,col="deepskyblue")
g <- g + geom_point(aes(color = movies),size = 2) 
g <- g + labs(x = "Number of movies per actor", y = "Actor's total gross revenue",title="Total Gross Revenue per actor by number of movies")
g
```

8 Average Gross Revenue per movie for actor by number of movies
```{r 8, echo=FALSE, cache=TRUE}
h <- ggplot(actors, aes(x = movies,y = actors$avRevenue))
h <- h + geom_hline(yintercept = 251,size=1,col="deepskyblue")
h <- h + geom_vline(xintercept = 18.58, size=1,col="deepskyblue")
h <- h + geom_point(aes(color = movies),size = 1) 
h <- h + labs(x = "Number of movies per actor", y = "Actor's total gross revenue",title="Average Gross Revenue per movie for actor by number of movies")
h
```

9 Top 25 movie cash cows
```{r 9, echo=FALSE, cache=TRUE}
library(plyr)
actorstopmovies <- actors[with(actors, order(-topMovieRevenue, -avRevenue)),]
dim(actorstopmovies)
colnames(actorstopmovies)
head(actorstopmovies, 25)
```

10 Bottom 25 IMDB #1 movies
```{r 10, echo=FALSE, cache=TRUE}
tail(actorstopmovies, 25)
```

11 Table Top 25 actor cash cows
```{r 11, echo=FALSE, cache=TRUE}
topactors <- actors[with(actors, order(-totalRevenue, -avRevenue)),]
head(topactors, 25)
```

12 Table Bottom 25 actor cash cows
```{r 12, echo=FALSE, cache=TRUE}
tail(topactors, 25)
```